---
title: "Final Exam FlexDashboard Kel A"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: yeti
    source_code: embed
---

```{r setup, include=FALSE}
# Importing libraries
library(flexdashboard)
library(tidyverse)
library(highcharter)
library(gt)
library(htmltools)
library(viridis)
library(DT)
library(ggplot2)
library(sunburstR)
library(lubridate)
library(plotly)
library(ggplot2)
```

```{r}
# This is going to be a datatable
cust <- read.csv("Customers.csv", sep = ",")
ord <- read.csv("Orders.csv", sep = ",")
orddet <- read.csv("OrderDetails.csv", sep = ",")
emp <- read.csv("Employees.csv")
pro <- read.csv("Products.csv", sep = ",")
ship <- read.csv("Shippers.csv", sep = ",")
cat <- read.csv("Categories.csv", sep = ",")
supp <- read.csv("Suppliers.csv")
```


Table {data-orientation=rows}
=======================================================================

## Column {.tabset .tabset-fade data-height=520}
-----------------------------------------------------------------------

### Customers {data-height=520}

```{r}
datacust <- merge(
  x = cust,
  y = ord,
  by = "CustomerID",
  all.x = TRUE,
  all.y = TRUE
)

datacust <- merge(
  x = datacust,
  y = orddet,
  by = "OrderID",
  all.x = TRUE,
  all.y = TRUE
)

datacust <- merge(
  x = datacust,
  y = pro,
  by = "ProductID",
  all.x = TRUE,
  all.y = TRUE
)

datatable(datacust, 
          options=list(scrollX=TRUE),
          caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    'Table: ', htmltools::em('Information of Customers')
  ))
```


### Suppliers {data-height=520}

```{r}
datasup <- merge(
  x = supp,
  y = pro,
  by = "SupplierID",
  all.x = TRUE,
  all.y = TRUE
)

datasup <- merge(
  x = datasup,
  y = orddet,
  by = "ProductID",
  all.x = TRUE,
  all.y = TRUE
)

datatable(datasup, 
          options=list(scrollX=TRUE),
          caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    'Table: ', htmltools::em('Information of Suppliers')
  ))
```


### Employees {data-height=520}

```{r}
dataemp <- merge(
  x = emp,
  y = ord,
  by = "EmployeeID",
  all.x = TRUE,
  all.y = TRUE
)

dataemp <- merge(
  x = dataemp,
  y = orddet,
  by = "OrderID",
  all.x = TRUE,
  all.y = TRUE
)

dataemp <- merge(
  x = dataemp,
  y = pro,
  by = "ProductID",
  all.x = TRUE,
  all.y = TRUE
)

datatable(dataemp, 
          options=list(scrollX=TRUE),
          caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    'Table: ', htmltools::em('Information of Employees')
  ))
```


### Shippers {data-height=520}

```{r}
dataship <- merge(
  x = ord,
  y = orddet,
  by = "OrderID",
  all.x = TRUE,
  all.y = TRUE
)

dataship <- merge(
  x = dataship,
  y = ship,
  by = "ShipperID",
  all.x = TRUE,
  all.y = TRUE
)

datatable(dataship, 
          options=list(scrollX=TRUE),
          caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    'Table: ', htmltools::em('Information of Shippers')
  ))
```


### Categories {data-height=520}

```{r}
datacat <- merge(
  x = datacust,
  y = cat,
  by = "CategoryID",
  all.x = TRUE,
  all.y = TRUE
)

datatable(datacat, 
          options=list(scrollX=TRUE),
          caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    'Table: ', htmltools::em('Information of Catagories')
  ))
```



Customer-chart {data-orientation=rows}
=======================================================================


## Column {.tabset .tabset-fade data-height=520}
-----------------------------------------------------------------------

### Average Purchase {data-width=1200}

```{r fig.height=5}
custom_colors <- viridis::turbo(n = 15)

datacust %>% 
  group_by(CustomerName) %>% 
  summarise(Purchase = mean(Quantity*Price)) %>% 
  arrange(desc(Purchase)) %>% 
  head(15) %>% 
  hchart('column', hcaes(x = CustomerName, y = Purchase,color = custom_colors)) %>%   hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>Average Purchase: </b> {point.y} <br>') %>% 
  hc_title(text = 'Most Average of Customer Purchase',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'By Money that Customer Spend in our Store',
              style = list(fontSize = '16px')) %>% 
  hc_credits(enabled = TRUE, text = '@diyasarya')
```

### Weekly Sold {data-width=1200}

```{r fig.height=5}
theme_set(theme_minimal())
topquan <- datacust %>%
  group_by(OrderDate) %>%
  summarise(Quantity = sum(Quantity)) %>%
  arrange(OrderDate) 

hc <- topquan %>%
  hchart('line', hcaes(x = OrderDate, y = Quantity)) %>%
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>Number of Quantity: </b> {point.y} <br>') %>% 
  hc_title(text = 'Weekly Product Sold',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'By Number of Quantity',
              style = list(fontSize = '16px')) %>% 
  hc_credits(enabled = TRUE, text = '@diyasarya')
hc
```


Supplier-chart {data-orientation=rows}
=======================================================================


## Column {.tabset .tabset-fade data-height=520}
-----------------------------------------------------------------------

### Most Required Suppliers {data-width=1200}

```{r fig.height=5}
custom_colors <- viridis::turbo(n = 15)

datasup %>% 
  group_by(SupplierName) %>% 
  summarise(Quantity = sum(Quantity)) %>% 
  arrange(desc(Quantity)) %>% 
  head(15) %>% 
  hchart('column', hcaes(x = SupplierName, y = Quantity,color = custom_colors)) %>%   hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>Number of Reviews: </b> {point.y} <br>') %>% 
  hc_title(text = 'Most Required Suppliers',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'By Number of Quantity',
              style = list(fontSize = '16px')) %>% 
  hc_credits(enabled = TRUE, text = '@sausanramadhani')
```


### Most Suppliers Country {data-width=1200}

```{r fig.height=5}
country_count <- datasup %>%
  group_by(Country) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
sup1 <- country_count %>% 
  ggplot(aes(x = count,
             y = reorder(Country, count),
             fill = count)) +
  geom_col() +
  scale_fill_gradient(low = "red", high = "black") +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = 'Most Suppliers Country' ,
       x = 'Suppliers Count',
       y = NULL)
ggplotly(sup1)
```


Employee-chart {data-orientation=rows}
=======================================================================


## Column {.tabset .tabset-fade data-height=520}
-----------------------------------------------------------------------

### Revenue Earn {data-width=1200}

```{r fig.height=5}
dataemp$revenue = dataemp$Quantity*dataemp$Price

emp1 <- dataemp %>% 
  group_by(FirstName) %>%
  summarise(revenue = sum(revenue)) %>%
  ggplot(aes(x = revenue,
             y = reorder(FirstName, revenue),
             color = revenue,
             text = FirstName)) +
  geom_segment(aes(x = 0, xend = revenue, yend = FirstName), size = 1) +
  geom_point(size = 3) +
  labs(x = 'Revenue',
       y = NULL,
       title = 'Revenue Earned by Each Employee') +
  scale_color_gradient(low = "red", high = "black") +
  scale_x_continuous(labels = scales::comma) +
  theme_minimal() +
  theme(legend.position = "none",
        plot.margin = margin(r = 20))

ggplotly(emp1, tooltip = "text")
```


### Average Purchase {data-width=1200}

```{r fig.height=5}
dataemp$revenue = dataemp$Quantity*dataemp$Price
hc <- dataemp %>%
  group_by(OrderDate) %>%
  summarise(revenue = sum(revenue)) %>%
  hchart('line', hcaes(x = OrderDate, y = revenue)) %>%
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>Number of Quantity: </b> {point.y} <br>') %>% 
  hc_title(text = 'Weekly Revenue Earn',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'By Number of Revenue',
              style = list(fontSize = '16px')) %>% 
  hc_credits(enabled = TRUE, text = '@sausanramadhani')
hc
```


Shipper dan Categories-chart {data-orientation=rows}
=======================================================================


### Delivery Service Usage {data-width=600 data-height=510}

```{r fig.height=5}
# Colors
custom_colors <- viridis::inferno(n = 3)

# Most popular artists by weeks on board
dataship %>% 
  group_by(ShipperName) %>% 
  summarise(Quantity = sum(Quantity)) %>% 
  arrange(desc(Quantity)) %>% 
  head() %>% 
  hchart('pie', hcaes(x = ShipperName, y = Quantity, color = custom_colors),innerSize = 200) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>Number of Delivery Service Usage: </b> {point.y} <br>') %>% 
  hc_title(text = 'Most Popular Shipper',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'By Number of Delivery Service Usage',
              style = list(fontSize = '16px')) %>% 
  hc_credits(enabled = TRUE, text = '@diyasarya')
```

### Most Categories {data-width=600 data-height=510}

```{r}
daa <- datacat %>%
  select(CategoryName, Quantity) %>%
  group_by(CategoryName) %>%
  summarise(Quantity = sum(Quantity))
sunburst(daa)
```
